Spfy: an integrated graph database and analysis platform for real-time prediction of Escherichia coli phenotypes

### 2018-02-28 paper-webserver.tex
ADD: a la phylo

% 2. Big Problem: but tools are for individual analysis
The rapid characterization and comparison of bacterial pathogens relies principally on the combination of outputs from multiple software programs that are targeted for specific applications. Examples include the identification of known antimircrobial (AMR) resistance genes, through software such as the Resistance Gene Identifier (RGI) \cite{mcarthur2013comprehensive}, {ResFinder}, {ARG-ANNOT}, and {ARIBA}; or the identification of known virulence genes through software such as VirulenceFinder \cite{kleinheinz2014applying}, {SRST2}, and {an additional reference}. \todo{Add a section on serotyping and subtyping a la Phylotyper}. These methods represent \textit{in-silico} analogues of traditional wet-lab tests, which allows new WGS results to be viewed in the context of historical tests, and greatly expedites the analyses of newly sequenced genomes.

>>>>

% 2. Big Problem: but tools are for individual analysis
The rapid characterization and comparison of bacterial pathogens relies principally on the combination of outputs from multiple software programs that are targeted for specific applications. Examples include the identification of known antimircrobial resistance (AMR) genes, through software such as the Resistance Gene Identifier (RGI) \cite{mcarthur2013comprehensive}, \cite{kleinheinz2014applying}, \cite{gupta2014arg}, and ARIBA \cite{hunt2017ariba}; or the identification of known virulence factor genes (VF) through software such as VirulenceFinder \cite{kleinheinz2014applying}, SRST2 \cite{inouye2014srst2}, and GeneSippr \cite{lambert2015genesippr}. For clinical diagnoses and comparisons, individual species can be first divided into subtypes with complementing AMR and VF results. Software methods for subtyping rely on intraspecies genes or genomic regions, and are targeted through software such as Phylotyper \cite{whiteside2017phylotyper}, SerotypeFinder \cite{joensen2015rapid}, the EcOH dataset applied through SRST2 \cite{ingle2016silico}, and V-Typer \cite{carrillo2016comparative}. These methods represent \textit{in-silico} analogues of traditional wet-lab tests, which allows new WGS results to be viewed in the context of historical tests, and greatly expedites the analyses of newly sequenced genomes.
